---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# awhina

<!-- badges: start -->
[![R-CMD-check](https://github.com/lddurbinAC/awhina/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/lddurbinAC/awhina/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of awhina is to support kaimahi at Auckland Council when they work with the R programming language.

## Installation

You can install the development version of awhina from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lddurbinAC/awhina")
```

## Example

This is a basic example which shows you how to install and load the most useful R packages (known collectively as the tidyverse),
and how to store and retrieve that path to your team's locally-sync'd SharePoint Document Library.

```{r example}
library(awhina)
get_started("tidyverse")

create_environment_variable("path/to/my/sharepoint/directory")
my_files <- get_file_storage_path()
```
